On the probability of finding a nonphysical solution through shadowing

### 2020-10-27 main.tex
Arxiv version 2

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. \email{nishac@mit.edu 
           }
}

@@

In view of the plucked tent map, we can question further the
validity of numerical solutions. Can numerical play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations that nevertheless 
exhibit drastically different statistics from that of the ensemble? Uniformly hyperbolic 
dynamical systems exhibit \emph{linear response} 
(\cite{ruelle}\cite{baladi}) by which small parameter perturbations 
lead to small changes in statistics, which can be expanded as Taylor series around the reference parameter value. But, uniform hyperbolicity is a mathematical idealization, and although some physical systems have been observed to behave as if they were uniformly hyperbolic \cite{gallavotti}, a violation of uniform hyperbolicity is more likely 
\cite{wormell}\cite{luca}. Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic cause significant change in the stationary probability distribution on the attractor. The plucked tent map adds to this list of examples by exhibiting a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}).

>>>>

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. \email{nishac@mit.edu 
		   }  \email{qiqi@mit.edu}
}

@@

In view of the plucked tent map, we can question further the
validity of numerical solutions. Can numerical play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations that nevertheless 
exhibit drastically different statistics from that of the ensemble? Uniformly hyperbolic 
dynamical systems exhibit \emph{linear response} 
(\cite{ruelle}\cite{baladi}) by which small parameter perturbations 
lead to small changes in statistics, which can be expanded as Taylor series around the reference parameter value. But, uniform hyperbolicity is a mathematical idealization, and although some physical systems have been observed to behave as if they were uniformly hyperbolic \cite{gallavotti}, a violation of uniform hyperbolicity is more likely 
\cite{wormell}\cite{luca}. Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic causes significant change in the stationary probability distribution on the attractor. The plucked tent map adds to this list of examples by exhibiting a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}).
